Drivers of sex differences in consumption

### 2017-06-22 sex-difference/sex-difference.Rmd
sex diff

>>>>

## Margins of azithromycin consumption

Maybe women take more azithromycin because usage is more concentrated in women than in men. Then we could explain the increased consumption by a small number of people taking more drug. (Yonatan points to Lady Windmere syndrome.) In fact, consumption is more even among women. As always, this is driven by the extensive fraction: more women took at least one dose:

```{r}
pde %>%
  filter(drug=='azithromycin') %>%
  count(bene_id) %>% rename(n=n_azi) %>%
  right_join(bene, by='bene_id') %>% replace_na(list(n_azi=0)) %>%
  count(sex, n_azi) %>%
  group_by(sex) %>%
  mutate(f_ppl=n/sum(n), cum_f_ppl=cumsum(f_ppl),
         cum_cons=cumsum(n_azi*n), cum_f_cons=cum_cons/max(cum_cons)) %>%
  ggplot(aes(x=cum_f_ppl, y=cum_f_cons, color=sex)) +
  geom_point() +
  geom_line() +
  xlab('Fraction of consumers') + ylab("Fraction of that sex's azithromycin consumed")
```
